### 2019-11-25 ChapterResults/chapterResults.tex
Updated: Minor tweaks to results chapter

Relative speed is controlled such that the two objects used in the experiment collide with each other with that relative speed. Latency is controlled using the Traffic Manager tool to emulate latency for all communications between the servers. Half of the desired latency is applied to each server, resulting in the total desired latency between servers.
Frame-time is controlled using a wait within the simulation's update loop, this is limited to a target frame-time as the resultant frame-times are a normal distribution with the target frame-time as the median. This means half of all frames are expected to be above the target frame-time, which may cause false-positives in the following experiments, however the variance in frame-time is low, so false-positives are expected to be rare.

@@

The collision point of the objects has a small random variation of point along the collision axis and the collision time of the two objects is also varied by $10$ physics time-steps to prevent producing exactly the same results each iteration, but the two objects will always collide while one of the objects is intersecting the server region boundary.

The two servers use the same tolerances used in the performance experiments, a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$, maximum latency tolerance of $2ms$ and a maximum frame-time of $15ms$. Each experiment is repeated $10$ times.

@@

\subsubsection{Evaluation}
The varying factors experiments demonstrate that the aura calculation is either correct or close to correct for all aura tolerance factors. For each varied factor below the tolerance value there are only a small number of erroneous collisions just below the tolerance value and no missed collisions. Once factors increase above the tolerance value erroneous collisions begin to occur with increasing number and magnitude.

@@

In addition to varying each aura tolerance factor, an experiment was also carried out to determine the effects of packet-loss on the correctness of collisions between objects. In this experiment the packet-loss was varied from $0\%$ to $80\%$ in increments of $10\%$. Packet-loss is not factored into the aura calculation and therefore has no tolerance. Packet-loss is controlled using the Traffic Manager tool; packet-loss is emulated on each server for all communication received from the other server.

>>>>

Relative speed is controlled such that the two objects used in the experiment collide with each other with that relative speed. Latency is controlled using the Traffic Control tool to emulate latency for all communications between the servers. The desired latency is applied as a fixed delay to each server, resulting in that delay being applied to all packets outgoing from that server. Frame-time is controlled using a wait within the simulation's update loop, this is limited to a target frame-time as the resultant frame-times are a normal distribution with the target frame-time as the median. This means half of all frames are expected to be above the target frame-time, which may cause false-positives in the following experiments, however the variance in frame-time is low, so false-positives are expected to be rare.

@@

The two servers use the same tolerances used in the performance experiments, a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$, maximum latency tolerance of $2ms$ and a maximum frame-time of $15ms$. Each server has a random delay between $0$ and the target frame-time in order to prevent the two servers always having synchronous update cycles. Each experiment is repeated $10$ times.

@@

\subsubsection{Evaluation}
%TODO: The following needs to be formalised.
The varying factors experiments demonstrate that the aura calculation is either correct or close to correct for all aura tolerance factors. For each varied factor below the tolerance value there are only a small number of erroneous collisions just below the tolerance value and no missed collisions. Once factors increase above the tolerance value erroneous collisions begin to occur with increasing number and magnitude.

If the aura calculation factors remain within their respective tolerances, erroneous collisions will be small in magnitude and rare in number. %TODO: Summary Table: Row for each factor: Number of collisions below tolerance, Percentage of errors below tolerance, Mean error below tolerance

%Which factors leads to greatest:
%Ratio of errors - Relative Speed 90%+ >110m/s
%Magnitude of errors (overall) - Relative Speed
%Magnitude of errors (just errors) - Relative Speed
%Max Error - Relative Speed

@@

In addition to varying each aura tolerance factor, an experiment was also carried out to determine the effects of packet-loss on the correctness of collisions between objects. In this experiment the packet-loss was varied from $0\%$ to $80\%$ in increments of $10\%$. Packet-loss is not factored into the aura calculation and therefore has no tolerance. Packet-loss is controlled using the Traffic Control tool; packet-loss is emulated on each server for all communication received from the other server.
